### 2022-04-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@c76a7e0665deb15a003729157cf1313d9efbce37 🚀

Main idea here: we have interaction information for some subset of the
species pool, and good SDMs for a different subset of the species pool.
There is some overlap in these species poolsHow do we combine this to
predict: species interactions, uncertainty in interactions (which as
increases indicates better use of sampling time).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling (Olesen \emph{et al.} 2011).
\end{enumerate}

>>>>

Main idea here: we have interaction information for some subset of the
species pool, and good SDMs for a different subset of the species pool.
There is some overlap in these species pools. How do we combine this to
predict: species interactions, uncertainty in interactions (which as
increases indicates better use of sampling time).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological and spatial uncoupling (Olesen \emph{et al.} 2011).
\end{enumerate}
